---
title: "Homework 1 - MSCI 701"
author: "Graham C. McLaughlin"
date: "2023-01-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.asp = 0.618, collapse=TRUE)

```

Below I summarized my sleep schedule to determine if the time I wake up (wake_time variable) and how long it takes me to wake up (measured by num_of_snoozes variable) has an effect the likelihood of me making it to the gym.

```{r data, echo = FALSE, results='asis'}
my_data <- read.table(file = "hw_1_data.txt", header = TRUE)
library(knitr)
kable(my_data, caption = "My Data:")
```

As it turns out, since I never went to the gym in the last 10 days (except where num_of_gym_trips = 0.5, where I walked to the gym, realized I forgot my headphones, and walked back home), there is no correlation between wake_time or num_of_snoozes and the likelihood of making it to the gym. Summary statistics are summarized below:

```{r summary, echo = TRUE}
summary(my_data)
## Mean num_of_snoozes:
mean(my_data$num_of_snoozes)
## Mean wake_time:
mean(my_data$wake_time)
```